Supplement 2

### 2020-10-30 paper/supplement-2.Rmd
add supplement 2 changes

@@

extractions <- tibble( # This is Table 2
  `Missing data reported` = "XX",
  `Type of missingness reported (i.e., MCAR, MAR or MNAR)` = "XX",
  `Missing data explored` = "XX",
  `Missing observations imputed` = "XX",
  `Imputation method` = "XX",
  `Data shared` = "XX"
)

@@

>>>>

```{r}
gs_football_missings_stated  <- gs_football_final_matches %>% 
  filter(any_missing_data_statement == 1)
```

```{r}
gs_football_binom_statement <- gs_football_missings_stated %>% 
  football_binom_confint(any_statement_about_mcar_mnar_mar)  %>% 
  percent_binom_conf()

gs_football_binom_explored <- gs_football_missings_stated %>% 
  football_binom_confint(were_missing_data_explored)  %>% 
  percent_binom_conf()

gs_football_binom_imputation <- gs_football_missings_stated %>% 
  football_binom_confint(was_imputation_used) %>% 
  percent_binom_conf()

```{r}
report_cis <- function(var){
  ci_mean <- var$mean_pct
  ci_upper <- var$lower_pct
  ci_lower <- var$upper_pct

  glue::glue("{var$mean_pct} \\
           [{var$lower_pct} - \\
           {var$upper_pct}]")
}
```

@@

extractions <- tibble( # This is Table 2
  `Type of missingness reported (i.e., MCAR, MAR or MNAR)` = report_cis(gs_football_binom_statement),
  `Missing data explored` = report_cis(gs_football_binom_explored),
  `Missing observations imputed` = report_cis(gs_football_binom_imputation)
)

# pivot_then
extractions

knitr::kable(extractions)

@@

There were `r nrow(gs_football_missings_stated)` studies that provided some statement about missing data
